---
title: "README"
output: github_document
date: "2024-02-05"
---

```{r, include=FALSE, cache = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "README_files/figures/", 
  out.width = "100%",
  cache = FALSE)

asciicast::init_knitr_engine(
  startup = quote({
    library(icampcolors)
    set.seed(1) }),
  echo = TRUE,
  echo_input = FALSE
)
```

## iCaMP Color Palette

Color palettes developed by Zachary Milstone, MD/PhD for use by the integrative Cardiovascular Metabolism and Pathophysiology (iCaMP) Program. Many of these palettes are colorblind friendly and have been developed for use in conference and publication figures.

This package was created using the [Creating a colour palette package vignette](https://mccarthy-m-g.github.io/palettes/articles/creating-packages.html) and the [palettes Package](https://mccarthy-m-g.github.io/palettes/index.html), both developed by Michael McCarthy. Here are additional resources used in the development of this package:

- [sunsets Package developed by Michael McCarthy](https://github.com/mccarthy-m-g/sunsets)
- [R Packages (2e) by Hadley Wickham & Jennifer Bryan](https://r-pkgs.org/)
- [A Helpful Way to Install R Packages Hosted on GitHub](https://cran.r-project.org/web/packages/githubinstall/vignettes/githubinstall.html)


## Included Palettes
```{r echo = FALSE}
plot(icampcolors::icamp_color_palettes)
```

## Installation

You can install icampcolors from [Github](https://github.com/) by doing the following:



```{r, echo = TRUE}

library(devtools)

devtools::install_github("jcunha2023/icampcolors")

```

##Usage

```{r, echo = TRUE}

library(icampcolors)
```


icampcolors includes a distinct iCaMP blue color palette, a discrete fluorescent color palette, a colorblind-friendly discrete color palette, and six sequential color palettes. These can be accessed from the following R objects:

- icamp_blue_discrete for the unique iCaMP blue color
- icamp_colorblind_friendly_discrete for the colorblind friendly palette
- icamp_palettes_sequential for the sequential palettes
-icamp_color_palettes for all palettes

You can preview the palettes in the console by printing them:

```{r, echo = FALSE}
icamp_palettes_sequential
```

Preview the palettes in the Plots pane with plot():

```{r}
plot(icamp_palettes_sequential)
```

Subset palettes using [, [[, and $.
  - To extract one or more palettes use [:
  
```{r}
icamp_palettes_sequential[c("blue", "bright")]
```

To get palette names use names():

```{r}
names(icamp_palettes_sequential)
```

  

