---
title: "README"
output: github_document
date: "2024-02-05"
---

```{r setup, include=FALSE, cache = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#")

asciicast::init_knitr_engine(
  startup = quote({
    library(icampcolors)
    set.seed(1)
  }), 
  echo = TRUE, 
  echo_input = FALSE
)
```

## iCaMP Color Palette

Color palettes developed by Zachary Milstone, MD/PhD for use by the integrative Cardiovascular Metabolism and Pathophysiology (iCaMP) Program. Many of these palettes are colorblind friendly and have been developed for use in conference and publication figures.

This package was created using the [Creating a colour palette package vignette](https://mccarthy-m-g.github.io/palettes/articles/creating-packages.html) and the [palettes Package](https://mccarthy-m-g.github.io/palettes/index.html), both developed by Michael McCarthy. Here are additional resources used in the development of this package:

- [sunsets Package developed by Michael McCarthy](https://github.com/mccarthy-m-g/sunsets)
- [R Packages (2e) by Hadley Wickham & Jennifer Bryan](https://r-pkgs.org/)
- [A Helpful Way to Install R Packages Hosted on GitHub](https://cran.r-project.org/web/packages/githubinstall/vignettes/githubinstall.html)


## Included Palettes
```{r echo = FALSE}
plot(icampcolors::icamp_color_palettes)
```
