---
title: "README"
output: github_document
date: "2024-02-05"
---

```{r, include=FALSE, cache = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "README_files/figures/", 
  out.width = "100%",
  cache = FALSE,
   asciicast_theme = "pkgdown")

asciicast::init_knitr_engine(
  startup = quote({
    library(icampcolors)
    set.seed(1)}),
  echo = TRUE,
  echo_input = FALSE
)
```

## iCaMP Color Palette

Color palettes developed by Zachary Milstone, MD/PhD for use by the integrative Cardiovascular Metabolism and Pathophysiology (iCaMP) Program. Many of these palettes are colorblind friendly and have been developed for use in conference and publication figures.

This package was created using the [Creating a colour palette package vignette](https://mccarthy-m-g.github.io/palettes/articles/creating-packages.html) and the [palettes Package](https://mccarthy-m-g.github.io/palettes/index.html), both developed by Michael McCarthy. Here are additional resources used in the development of this package:

-   [sunsets Package developed by Michael McCarthy](https://github.com/mccarthy-m-g/sunsets)
-   [R Packages (2e) by Hadley Wickham & Jennifer Bryan](https://r-pkgs.org/)
-   [A Helpful Way to Install R Packages Hosted on GitHub](https://cran.r-project.org/web/packages/githubinstall/vignettes/githubinstall.html)

## Included Palettes

```{r echo = FALSE}
library(icampcolors)
plot(icampcolors::icamp_color_palettes)
```


## Installation

You can install icampcolors from [Github](https://github.com/) by doing the following:

```{r}

library(devtools)

devtools::install_github("jcunha2023/icampcolors")

```

## Usage

```{r echo = TRUE}

library(icampcolors)
```

icampcolors includes a distinct iCaMP blue color palette, a discrete fluorescent color palette, a colorblind-friendly discrete color palette, and six sequential color palettes. These can be accessed from the following R objects:

-   icamp_palettes_discrete for the sequential plettes
-   icamp_palettes_sequential for the sequential palettes 
-icamp_color_palettes for all palettes

You can preview the palettes in the console by printing them:

```{asciicast icamp_palettes_sequential}
icamp_palettes_sequential
```

Preview the palettes in the Plots pane with plot():

```{r echo = FALSE}
plot(icamp_palettes_sequential)
```

Subset palettes using [, [[, and \$. - To extract one or more palettes use [:

```{r echo = TRUE}
icamp_palettes_sequential[c("blue", "bright")]
```

To get palette names use names():

```{r echo = FALSE}
names(icamp_palettes_sequential)
```


## Example Use Cases

```{r echo = FALSE}
library(icampcolors)
library(ggplot2)
library(scales)
library(dplyr)
library(gt)
```


Using the Iris data set, you can display data points in iCaMP Blue:

```{r echo = TRUE}

setosa_data <- subset(iris, Species == "setosa")

ggplot(setosa_data, aes(Sepal.Length, Petal.Width))+
  geom_point(aes(color = Species))+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_color_palette_d(icamp_palettes_discrete$icamp_blue)
```

Here is an example of generating a heatmap with a diverging color palette using the faithfuld data set:

```{r echo = TRUE}

ggplot(faithfuld, aes(eruptions, waiting, fill = density))+
  geom_tile()+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_fill_palette_c(icamp_color_palettes$diverging_1)
```

If you want a specific color from a palette, you can use indexing to access the hex code:


```{r echo = TRUE}

setosa_data <- subset(iris, Species == "setosa")

ggplot(setosa_data, aes(Sepal.Length, Petal.Width))+
  geom_point(aes(color = Species))+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_color_palette_d(icamp_palettes_discrete$icamp_blue)
```

Here is an example of generating a heatmap with a diverging color palette using the faithfuld data set:

```{r echo = TRUE}

setosa_data <- subset(iris, Species == "setosa")

ggplot(setosa_data, aes(Sepal.Length, Petal.Width))+
  geom_point(aes(color = Species))+
  scale_color_palette_d(icamp_color_palettes$fluro[4])
```


Finally, icampcolors can be used with non-ggplot data visualization tools in R. Here is an example of a table displaying air quality metric, with the bright color palette used to fill the temperature cells:

```{r echo = TRUE}

# Modify the `airquality` dataset by adding the year
# of the measurements (1973) and limiting to 10 rows
airquality_m <- 
  airquality %>%
  mutate(Year = 1973L) %>%
  slice(1:10) %>% 
  select(Year, Month, Day, Temp)

# Create a display table using the `airquality`
# dataset; arrange columns into groups
gt_tbl <- 
  gt(airquality_m) %>%
  tab_header(
    title = "New York Temperature Measurements",
    subtitle = "Daily measurements in New York City (May 1-10, 1973)"
  ) %>%
  tab_spanner(
    label = "Time",
    columns = c(Year, Month, Day)
  ) %>%
  tab_spanner(
    label = "Measurement",
    columns = c(Temp)
  ) %>%
  cols_label(
    Temp = html("Temp,<br>&deg;F")
  )

# Show the gt table
gt_tbl

#pass color palette to vector

color_vector <- rev(icamp_palettes_sequential$bright)
character_vector <- as.character(color_vector)

gt_tbl %>% 
  data_color(
    columns = Temp,
    colors  = character_vector
  )

```


